Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-09 mtjournal.tex
added section on weight-tuning from outline

  (Go into details of per-genre differences here? or leave out, for
  space reasons?)

>>>>

  (Go into details of per-genre differences here? or leave out, for
  space reasons? -- leave out, I'd say)

\section{Weight-tuning to combine syntax and other knowledge sources}

TERp optimizer [Matt, a brief description here]

TERp comes with a variety of features (described earlier)

include optionally new features

Corpus: GALE 2.5 data, again documents randomly split into two groups,
evenly split across language and genre

tuning target: weighted correlation with mean-removed segment HTER

[we use weighted correlation to avoid emphasis on short segments
(which hurts document-level and system-level utility) ]

Select features from set:

\begin{description}
\item[E]: features from EDPM, specifically, P,R for inbound, outbound,
  full-links, and unlabeled links  (8 features)
\item[T]: features from basic TERp
  (inserts, deletes, substitutions, shifts)  (7 features)
\item[P]: features from TERp paraphraser
  (4 features)
\item[N]: precision and recall for 1-grams, 2-grams
\item[B]: brevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref)
\end{description}

tune weights on one set, test on the other (and vice versa).
reporting average r between the two.

\begin{verbatim}
   == Tuned For Weighted Mean Removed Pearson
     - Examining WGT_MEAN_RM_SEG_PEAR ==
            Average
      Cond   Test  
     ---------------
      ETPB   0.4096
      ETP    0.4038
      TPB    0.4010
      TP     0.3946
      TPNB   0.3940
      TPN    0.3891
      ETB    0.3871
      ET     0.3827
      TB     0.3815
      ETNB   0.3814
      ETN    0.3804
      T      0.3758
      TNB    0.3708
      TN     0.3680
      E      0.3287
      EB     0.3267
      ENB    0.3149
      NB     0.3058
      EN     0.2973
      N      0.2636
      B      0.1638
\end{verbatim}
(maybe don't report all these numbers!)

point: E+T $>$ T, E+TB $>$ TB, E+TP $>$ TP; information is available in
syntax that is not captured in the other measures.

point: syntax is *not* just an expensive way to get at n-grams;
N-grams are not the same -- TP $>$ TP+N, but TP $<$ TP+E
